Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
un comentario
Accepting advice and comments by @pacastillo

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype. As there was no available test data, a set of URL connection logs were provided by a Spanish company, % [Pedro] quizás decir que es una empresa de seguridad o algo así
as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}. % [Pedro] ¿ese "could be" se refiere a verbo en pasado? en ese caso, quizás usar "... was presented at..."
Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper. % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...

>>>>

To this end, MUSES analyses the users' behaviour by means of Data
Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
patterns which is later processed by means of Computational
Intelligence (CI) algorithms, namely Evolutionary Computation methods
\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
already presented in
\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
the implementation was in its early stages when those papers were
submitted. Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype. As there was no available test data, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented at \cite{mora14:urls}. % [Pedro] ¿ese "could be" se refiere a verbo en pasado? en ese caso, quizás usar "... was presented at..." % Gracias again
In this paper, once the first MUSES prototype has been released, and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them. % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
